High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-08 notebooks/mnist.qmd
robust net also added

@@

add_models = Dict(
    "LeNet-5" => lenet,
    "Large Ensemble (n=50)" => mlp_large_ens,
)

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble (n=50)", 
    "LeNet-5",
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```

```{julia}

```

>>>>

Robust Neural network:

```{julia}
mutable struct RobustNetBuilder
	n_hidden::Int
	lipschitz_bound::Float32
end

function MLJFlux.build(b::RobustNetBuilder, rng, n_in, n_out)
	n_hidden, γ = b.n_hidden, b.lipschitz_bound
    _n_hidden = fill(n_hidden,1)
    model_ps = DenseLBDNParams{Float32}(n_in, _n_hidden, n_out, γ; rng)
    chain = Flux.Chain(DiffLBDN(model_ps))
	return chain
end

# Final model:
rob_net = NeuralNetworkClassifier(
    builder=RobustNetBuilder(128, 5.0),
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)
```

Training all of them:

@@

add_models = Dict(
    "LeNet-5" => lenet,
    "RobustNet" => rob_net,
    "Large Ensemble (n=50)" => mlp_large_ens,
)

@@

measure = Dict(
    :f1score => multiclass_f1score, 
    :acc => accuracy, 
    :precision => multiclass_precision
)
model_performance = DataFrame()
for (mod_name, mod) in large_model_dict
    # Test performance:
    test_data = load_mnist_test()
    _perf = CounterfactualExplanations.Models.model_evaluation(mod, test_data, measure=collect(values(measure)))
    _perf = DataFrame([[p] for p in _perf], collect(keys(measure)))
    _perf.mod_name .= mod_name
    _perf.dataname .= "MNIST"
    model_performance = vcat(model_performance, _perf)
end
Serialization.serialize(joinpath(output_path,"mnist_model_performance_additional.jls"), model_performance)
CSV.write(joinpath(output_path, "mnist_model_performance_additional.csv"), model_performance)
model_performance
```

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble (n=50)", 
    "LeNet-5",
    "RobustNet",
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```
